Decentralized autonomous organization to automate governance\\ {\smaller \textbf{Final Draft - UNDER REVIEW}}

### 2016-04-14 paper/Paper.tex

To prevent this, the minority must always have the ability to retrieve their portion of the funds. Our solution is to allow a DAO to split into two. If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the ether before the proposal gets executed, they can submit and approve a special type of proposal to form a new DAO. The token holders that voted for this proposal can then split the DAO moving their portion of the ether to this new DAO, leaving the rest alone only able to spend their own money.

@@

Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens during at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
In order to avoid that possibility, all ether that is received above the initial Creation ratio of the token, will be sent to an extra account. Denoted as \verb|extraBalance| in \ref{app:TokenSale}. This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.

@@

    // The amount of days for which people who try to participate in the sale
    // by calling the fallback function will still get their money back
    uint constant saleGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed (used in the case `executeProposal`
    // fails because it throws)
    uint constant executeProposalPeriod = 5 days;

@@

    // Address of the Curator
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send money to
    mapping (address => bool) public allowedRecipients;

@@

    /// @dev This function is used to send money back
    /// to the DAO, it can also be used to receive payments that should not be
    /// counted as rewards (donations, grants, etc.)
    /// @return Whether the DAO received the ether successfully
    function receiveEther() returns(bool);

>>>>

To prevent this, the minority must always have the ability to retrieve their portion of the funds. Our solution is to allow a DAO to split into two. If an individual, or a group of token holders, disagree with a proposal and want to retrieve their portion of the ether before the proposal gets executed, they can submit and approve a special type of proposal to form a new DAO. The token holders that voted for this proposal can then split the DAO moving their portion of the ether to this new DAO, leaving the rest alone only able to spend their own ether.

@@

Creation ratio increases during the Creation Phase could lead to a situation where a single contributor, having bought tokens at the initial Creation ratio, could split the DAO immediately after the sale ends, thereby receiving more ether than they put in due to other contributors having a higher Creation ratio (\cite{GriffDiscussion}).
In order to avoid that possibility, all ether that is received above the initial Creation ratio of the token, will be sent to an extra account. Denoted as \verb|extraBalance| in \ref{app:TokenSale}. This ether can be sent back to the DAO through a proposal after the DAO has spent at least this amount of ether.
This rule is implemented in the internal function \verb|isRecipientAllowed| in section \ref{DAO}.

@@

    // The amount of days for which people who try to participate in the sale
    // by calling the fallback function will still get their ether back
    uint constant saleGracePeriod = 40 days;
    // The minimum debate period that a generic proposal can have
    uint constant minProposalDebatePeriod = 2 weeks;
    // The minimum debate period that a split proposal can have
    uint constant minSplitDebatePeriod = 1 weeks;
    // Period of days inside which it's possible to execute a DAO split
    uint constant splitExecutionPeriod = 27 days;
    // Period of time after which the minimum Quorum is halved
    uint constant quorumHalvingPeriod = 52 weeks;
    // Period after which a proposal can be closed (used in the case `executeProposal`
    // fails because it throws)
    uint constant executeProposalPeriod = 5 days;

@@

    // Address of the Curator
    address public curator;
    // The whitelist: List of addresses the DAO is allowed to send ether to
    mapping (address => bool) public allowedRecipients;

@@

    /// @dev This function is used to send ether back
    /// to the DAO, it can also be used to receive payments that should not be
    /// counted as rewards (donations, grants, etc.)
    /// @return Whether the DAO received the ether successfully
    function receiveEther() returns(bool);
